Repeatability of Pre-Flashover Fire Patterns on Gypsum Wall Board

### 2015-03-29 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex

\begin{table}
	\centering
	\begin{tabular}{|c|c|c|c|c|}
		\hline Density (kg/m$^3&)  &Thermal Conductivity   & Specific Heat  &  &  \\ 
		\hline   & Temperature ($^\circ$C) & (W/mK)  & Temperature ($^\circ$C)  & (kJ/kg $^\circ$C) \\ 
		\hline 807  & 24 	& 0.14 	&  		& 1.09 \\ 
		\hline  	& 100 	& 0.15  &  		&  \\ 
		\hline  	&  &  &  &  \\ 
		\hline 790 	& 20 	& 0.18	& 20 	& 0.90 \\ 
		\hline  	& 100 	& 0.15 	& 100 	& 0.90 \\ 
		\hline  	& 200 	& 0.13 	& 200 	& 0.80 \\ 
		\hline  	& 500 	& 0.15 	& 500	& 0.90 \\ 
		\hline 
		\end{tabular} 
		\caption[Thermal properties for 12.7~mm gypsum wallboard]{Thermal properties for 12.7~mm gypsum wallboard}
		\label{tab:Gypsum wallboard_Thermal_Properties}
		\end{table}

@@

 \begin{figure}[p]
 	\centering
 	\includegraphics[width=4.in]{../Figures/IWGB_NG_TC_Surface_Center_Avg}\\
 	\includegraphics[width=4.in]{../Figures/IWGB_NG_TC_Surface_Offset_Avg}\\
 	\includegraphics[width=4.in]{../Figures/IWGB_NG_TC_Plume_Avg}\\
 	\caption[Averaged peak wall and plume temperatures for the natural gas burner]{Averaged peak wall and plume temperatures for the natural gas burner fires at several different positions from the instrumented gypsum board wall.  The positions ranged from 0.3 m away from the wall to physically touching the wall, 0.0 m.}
 	\label{IWGB_NG_Temp_FrontSet}
 \end{figure}

\begin{figure}[p]
	\centering
	\includegraphics[width=4.5in]{../Figures/IWGB_NG_TC_Back_Center_Avg}\\
	\caption[Averaged peak temperatures on the backside of the gypsum board wall for the natural gas burner fires.]{Averaged peak temperatures along the vertical centerline of the backside of the gypsum board wall for the natural gas burner fires}
	\label{IWGB_NG_Temp_RearCenter}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=4.5in]{../Figures/IWGB_NG_HF_Center_Avg}\\
	\includegraphics[width=4.5in]{../Figures/IWGB_NG_HF_Offset_Avg}\\
	\caption[Averaged peak heat flux on the gypsum board wall for the natural gas burner fires.]{Averaged peak heat flux on the gypsum board wall along the vertical centerline and edge of the natural gas burner fires. }
	\label{IWGB_NG_HF_RearCenter}
\end{figure}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=4.in]{../Figures/IWGB_NG_TC_Surface_Center_Avg}\\
	\includegraphics[width=4.in]{../Figures/IWGB_GAS_TC_Surface_Center_Avg}\\
	\includegraphics[width=4.in]{../Figures/IWGB_PUF_TC_Surface_Center_Avg}\\
	\caption[Averaged centerline temperature for the natural gas, gasoline, and foam fires]{Averaged centerline temperature for the natural gas, gasoline, and foam fires. The number following the TC represents the height of thermocouple in decimeters  above the surface of the burner.}
	\label{IWGB_Temp_Comp_FrontCenter}
\end{figure}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=4.5in]{../Figures/IWGB_NG_HF_Center_Avg}\\
	\includegraphics[width=4.5in]{../Figures/IWGB_GAS_HF_Center_Avg}\\
	\includegraphics[width=4.5in]{../Figures/IWGB_PUF_HF_Center_Avg}\\
	\caption[Averaged centerline temperature for the natural gas, gasoline, and foam fires]{Averaged centerline temperature for the natural gas, gasoline, and foam fires. The number following the TC represents the height of thermocouple in decimeters  above the surface of the burner.}
	\label{IWGB_HF_Comp_Center}
\end{figure}

\begin{figure}[p]
	\centering
	\includegraphics[width=4.5in]{../Figures/IWGB_NG_HF_Offset_Avg}\\
	\includegraphics[width=4.5in]{../Figures/IWGB_GAS_HF_Offset_Avg}\\
	\includegraphics[width=4.5in]{../Figures/IWGB_PUF_HF_Offset_Avg}\\
	\caption[Averaged centerline temperature for the natural gas, gasoline, and foam fires]{Averaged centerline temperature for the natural gas, gasoline, and foam fires. The number following the TC represents the height of thermocouple in decimeters  above the surface of the burner.}
	\label{IWGB_HF_Comp_Edge}
\end{figure}

>>>>

\begin{table}
	\centering
	\begin{tabular}{|c|c|c|c|c|}
		\hline Density (kg/m$^3$)  & Thermal Conductivity   & Specific Heat  &  &  \\ 
		\hline   & Temperature ($^\circ$C) & (W/mK)  & Temperature ($^\circ$C)  & (kJ/kg $^\circ$C) \\ 
		\hline 807  & 24 	& 0.14 	&  		& 1.09 \\ 
		\hline  	& 100 	& 0.15  &  		&  \\ 
		\hline  	&  &  &  &  \\ 
		\hline 790 	& 20 	& 0.18	& 20 	& 0.90 \\ 
		\hline  	& 100 	& 0.15 	& 100 	& 0.90 \\ 
		\hline  	& 200 	& 0.13 	& 200 	& 0.80 \\ 
		\hline  	& 500 	& 0.15 	& 500	& 0.90 \\ 
		\hline 
		\end{tabular} 
		\caption[Thermal properties for 12.7~mm gypsum wallboard]{Thermal properties for 12.7~mm gypsum wallboard}
		\label{tab:Gypsum wallboard_Thermal_Properties}
		\end{table}

@@

 \begin{figure}[p]
 	\centering
 	\includegraphics[width=3.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg}\\
 	\includegraphics[width=3.5in]{../Figures/IWGB_NG_TC_Surface_Offset_Avg}\\
 	\includegraphics[width=3.5in]{../Figures/IWGB_NG_TC_Plume_Avg}\\
 	\caption[Averaged peak wall and plume temperatures for the natural gas burner]{Averaged peak wall and plume temperatures for the natural gas burner fires at several different positions from the instrumented gypsum board wall.  The positions ranged from 0.3 m away from the wall to physically touching the wall, 0.0 m.}
 	\label{IWGB_NG_Temp_FrontSet}
 \end{figure}

\begin{figure}[p]
	\centering
	\includegraphics[width=3.5in]{../Figures/IWGB_NG_TC_Back_Center_Avg}\\
	\caption[Averaged peak temperatures on the backside of the gypsum board wall for the natural gas burner fires.]{Averaged peak temperatures along the vertical centerline of the backside of the gypsum board wall for the natural gas burner fires}
	\label{IWGB_NG_Temp_RearCenter}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=3.5in]{../Figures/IWGB_NG_HF_Center_Avg}\\
	\includegraphics[width=3.5in]{../Figures/IWGB_NG_HF_Offset_Avg}\\
	\caption[Averaged peak heat flux on the gypsum board wall for the natural gas burner fires.]{Averaged peak heat flux on the gypsum board wall along the vertical centerline and edge of the natural gas burner fires. }
	\label{IWGB_NG_HF_RearCenter}
\end{figure}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=3.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg}\\
	\includegraphics[width=3.5in]{../Figures/IWGB_GAS_TC_Surface_Center_Avg}\\
	\includegraphics[width=3.5in]{../Figures/IWGB_PUF_TC_Surface_Center_Avg}\\
	\caption[Averaged centerline temperature for the natural gas, gasoline, and foam fires]{Averaged centerline temperature for the natural gas, gasoline, and foam fires. The number following the TC represents the height of thermocouple in decimeters  above the surface of the burner.}
	\label{IWGB_Temp_Comp_FrontCenter}
\end{figure}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=3.5in]{../Figures/IWGB_NG_HF_Center_Avg}\\
	\includegraphics[width=3.5in]{../Figures/IWGB_GAS_HF_Center_Avg}\\
	\includegraphics[width=3.5in]{../Figures/IWGB_PUF_HF_Center_Avg}\\
	\caption[Averaged centerline temperature for the natural gas, gasoline, and foam fires]{Averaged centerline temperature for the natural gas, gasoline, and foam fires. The number following the TC represents the height of thermocouple in decimeters  above the surface of the burner.}
	\label{IWGB_HF_Comp_Center}
\end{figure}

\begin{figure}[p]
	\centering
	\includegraphics[width=3.5in]{../Figures/IWGB_NG_HF_Offset_Avg}\\
	\includegraphics[width=3.5in]{../Figures/IWGB_GAS_HF_Offset_Avg}\\
	\includegraphics[width=3.5in]{../Figures/IWGB_PUF_HF_Offset_Avg}\\
	\caption[Averaged centerline temperature for the natural gas, gasoline, and foam fires]{Averaged centerline temperature for the natural gas, gasoline, and foam fires. The number following the TC represents the height of thermocouple in decimeters  above the surface of the burner.}
	\label{IWGB_HF_Comp_Edge}
\end{figure}
